Doppler Imaging Fun

### 2019-06-20 tex/gitlinks.tex
added luminosity attribute

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/3428daf248495c61773970e1703192fbe198cb85/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/3428daf248495c61773970e1703192fbe198cb85/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/3428daf248495c61773970e1703192fbe198cb85/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

>>>>

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/20af4c44c5da64772f41f1bf46eeb2d730a15e55/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/20af4c44c5da64772f41f1bf46eeb2d730a15e55/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/20af4c44c5da64772f41f1bf46eeb2d730a15e55/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

### 2019-06-20 tex/ms.tex
added luminosity attribute

If we take the inverse Fourier transform of Equation~(\ref{eq:fourier:S}),
we arrive at an expression for the observed spectrum:
%
\begin{align}
    \label{eq:convolve:SUgly1}
    S(\xi) 
    &=
    \mathcal{F}^{-1} \Bigg[\,\,\,
        \iint\limits_{\mathcal{S}(x, y)}
        \tilde{\bvec{p}}^\top(x, y)
        \mathrm{e}^{2\pi \imag k \alpha(x, y)}
        \mathrm{d}\mathcal{S}(x, y)
        \cdot
        \bvec{A_1}
        \cdot
        \bvec{\hat{a}}(k)
    \Bigg] \nonumber \\
    &=
    \mathcal{F}^{-1} \Bigg[\,\,\,
        \iint\limits_{\mathcal{S}(x, y)}
        \tilde{\bvec{p}}^\top(x, y)
        \mathrm{e}^{2\pi \imag k \alpha(x, y)}
        \mathrm{d}\mathcal{S}(x, y)
        \cdot
        \bvec{A_1}
    \Bigg]
    \circ
    \bvec{a}(\xi)
    \quad ,
\end{align}
%
where the second line follows from the convolution theorem, with
$\circ$ denoting the convolution operator over $\xi$ and 
$\bvec{a}(\xi) \equiv \mathcal{F}^{-1}\left[ \bvec{\hat{a}}(k) \right]$.
Since only the exponential term in the integrand depends on $k$, we may 
further simplify this expression:
%
\begin{align}
    \label{eq:convolve:SUgly2}
    S(\xi) 
    &=    
    \iint\limits_{\mathcal{S}(x, y)}
    \tilde{\bvec{p}}^\top(x, y)
    \mathcal{F}^{-1} \Big[
        \mathrm{e}^{2\pi \imag k \alpha(x, y)}
    \Big]
    \mathrm{d}\mathcal{S}(x, y)
    \cdot
    \bvec{A_1}
    \circ
    \bvec{a}(\xi)
    \nonumber \\
    &=    
    \iint\limits_{\mathcal{S}(x, y)}
    \tilde{\bvec{p}}^\top(x, y)
    \delta\big(\xi - \alpha(x, y)\big)
    \mathrm{d}\mathcal{S}(x, y)
    \cdot
    \bvec{A_1}
    \circ
    \bvec{a}(\xi)
    \quad,
\end{align}
%
where $\delta$ is the Dirac delta function. Since the integrand in the
equation above is zero everywhere except where the argument of the
$\delta$ function is zero, the equation may be written as a line integral 
along some curve $\mathcal{C}(x, y)$ whose points satisfy 
$\alpha(x, y) = \xi$
and lie within $\mathcal{S}$:
%
\begin{align}
    \label{eq:convolve:S}
    S(\xi) 
    &=    
    \mathbf{g}(\xi)
    \circ
    \bvec{a}(\xi)
    \quad,
\end{align}
%
where we define
%
\begin{align}
    \label{eq:convolve:g}
    \mathbf{g}(\xi) 
    &\equiv    
    \mathbf{s}^\top(\xi) 
    \cdot
    \bvec{A_1}
\end{align}
%
and
%
\begin{align}
    \label{eq:convolve:sT}
    \mathbf{s}^\top(\xi) 
    &\equiv    
    \int\limits_{\mathcal{C}(x, y)}
    \tilde{\bvec{p}}^\top(x, y)
    \mathrm{d}\mathcal{C}(x, y)
    \quad.
\end{align}

>>>>

If we take the inverse Fourier transform of Equation~(\ref{eq:fourier:S}),
we arrive at an expression for the observed spectrum:
%
\begin{align}
    \label{eq:convolve:SUgly1}
    S(\xi) 
    &=
    \mathcal{F}^{-1} \Bigg[\,\,\,
        \iint\limits_{\mathcal{S}(x, y)}
        \tilde{\bvec{p}}^\top(x, y)
        \mathrm{e}^{2\pi \imag k \alpha(x, y)}
        \mathrm{d}\mathcal{S}(x, y)
        \cdot
        \bvec{A_1}
        \cdot
        \bvec{\hat{a}}(k)
    \Bigg] \nonumber \\
    &=
    \mathcal{F}^{-1} \Bigg[\,\,\,
        \iint\limits_{\mathcal{S}(x, y)}
        \tilde{\bvec{p}}^\top(x, y)
        \mathrm{e}^{2\pi \imag k \alpha(x, y)}
        \mathrm{d}\mathcal{S}(x, y)
        \cdot
        \bvec{A_1}
    \Bigg]
    *
    \bvec{a}(\xi)
    \quad ,
\end{align}
%
where the second line follows from the convolution theorem, with
$\bvec{a}(\xi) \equiv \mathcal{F}^{-1}\left[ \bvec{\hat{a}}(k) \right]$
and $*$ denoting the convolution operator over $\xi$:
%
\begin{align}
    (f * g)(\xi) \equiv \int\limits_{-\infty}^{\infty}f(\tau)g(\xi - \tau)\mathrm{d}\tau
\end{align}
%
Since only the exponential term in the integrand depends on $k$, we may 
further simplify this expression:
%
\begin{align}
    \label{eq:convolve:SUgly2}
    S(\xi) 
    &=    
    \iint\limits_{\mathcal{S}(x, y)}
    \tilde{\bvec{p}}^\top(x, y)
    \mathcal{F}^{-1} \Big[
        \mathrm{e}^{2\pi \imag k \alpha(x, y)}
    \Big]
    \mathrm{d}\mathcal{S}(x, y)
    \cdot
    \bvec{A_1}
    *
    \bvec{a}(\xi)
    \nonumber \\
    &=    
    \iint\limits_{\mathcal{S}(x, y)}
    \tilde{\bvec{p}}^\top(x, y)
    \delta\big(\xi - \alpha(x, y)\big)
    \mathrm{d}\mathcal{S}(x, y)
    \cdot
    \bvec{A_1}
    *
    \bvec{a}(\xi)
    \quad,
\end{align}
%
where $\delta$ is the Dirac delta function. Since the integrand in the
equation above is zero everywhere except where the argument of the
$\delta$ function is zero, the equation may be written as a line integral 
along some curve $\mathcal{C}(x, y)$ whose points satisfy 
$\alpha(x, y) = \xi$
and lie within $\mathcal{S}$:
%
\begin{align}
    \label{eq:convolve:S}
    S(\xi) 
    &=    
    \mathbf{g}(\xi)
    *
    \bvec{a}(\xi)
    \quad,
\end{align}
%
where we define
%
\begin{align}
    \label{eq:convolve:g}
    \mathbf{g}(\xi) 
    &\equiv    
    \mathbf{s}^\top(\xi) 
    \cdot
    \bvec{A_1}
\end{align}
%
and
%
\begin{align}
    \label{eq:convolve:sT}
    \mathbf{s}^\top(\xi) 
    &\equiv    
    \int\limits_{\mathcal{C}(x, y)}
    \tilde{\bvec{p}}^\top(x, y)
    \mathrm{d}\mathcal{C}(x, y)
    \quad.
\end{align}
